Reliability Demonstration of A Novel Randomized Measurement and Verification Method for Switchable Control Retrofit Using Large-scale Public Dataset

### 2024-10-13 code/manuscript.Rmd
Adjust for NRE re-simulation

|                        |                                                                  |       |
|------------------|------------------------------------|------------------|
| Parameter              | Description                                                      | Value |
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

In this section, we demonstrate the influence of non-routine events
through two scenarios. In the first scenario, we quantified how much
occupancy would influence the electricity usage and added to the tidy
measurement set as they originally indicates no such change. In the
second scenario, we simply run the two M&V methods on the messy
measurement sets before adding the chilled water supply temperature
reset. Since no intervention is added, the more reliable method should
detect a 'saving' closer to 0.

>>>>

|                        |                                                                  |       |
|------------------|-----------------------------------|------------------|
| Parameter              | Description                                                      | Value |
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

We included two examples in this section to demonstrate the influence of
non-routine events on M&V savings. In the first scenario, we manually
subtracted a certain amount of electricity usage for a period of time
quantified how much occupancy would influence the electricity usage and
added to the tidy measurement set as they originally indicates no such
change. In the second scenario, we simply run the two M&V methods on the
messy measurement sets before adding the chilled water supply
temperature reset. Since no intervention is added, the more reliable
method should detect a 'saving' closer to 0.
